Viscous Transport in Eroding Porous Media

### 2019-08-25 docs/transport/erosion_transport.tex
add a new figure in transport paper

Next, we use the 1000 tracer trajectories to compute the first
(Figure~\ref{fig:Eroding100anomalous}(a)) and second
(Figure~\ref{fig:Eroding100anomalous}(b)) moments of the streamlines at
various porosities.  At high porosities, the first moment is similar to
the first-moment of trajectories in a empty channel (black dashed line).
At smaller porosities, the first moment is always linear, but larger
slopes indicate that the length of the trajectories are longer at lower
porosities \todo[inline]{Don't understand how this is the case}.  The
onset of anomalous dispersion is observed in
Figure~\ref{fig:Eroding100anomalous}(b). At early times, the particle
spreading is comparable to that of an open channel (dashed curve)
corresponding to the ballistic regime.  However, as the trajectories
traverse the geometry, a transition to a super-dispersive case,
especially at low porosities, is evident.  The dashed-dotted line
corresponds has a slope less than 1 indicating the long time behavior of
the trajectories
\begin{align*}
  \sigma_\lambda \sim t^{0.8715}.
\end{align*}

\begin{figure}[H]
\center
\includegraphics*[width =0.45\linewidth]{./figs/100b_first_moment}
\includegraphics*[width =0.45\linewidth]{./figs/100b_second_moment}
\caption{\label{fig:Eroding100anomalous} The first and second moments of
trajectories passing through an eroding geometry at several porosities.
The dashed black line corresponds to a porosity of 100\%, and the
dashed-dotted line is a line of best fit with slope 0.8715.}
\end{figure}

>>>>

Next, we use the 1000 tracer trajectories to compute the second
(Figure~\ref{fig:Eroding100anomalous}) moments of the streamlines at
various porosities.  At high porosities, the first moment is similar to
the first-moment of trajectories in a empty channel (black dashed line).
At smaller porosities, the first moment is always linear, but larger
slopes indicate that the length of the trajectories are longer at lower
porosities \todo[inline]{Don't understand how this is the case}.  The
onset of anomalous dispersion is observed in
Figure~\ref{fig:Eroding100anomalous}. At early times, the particle
spreading is comparable to that of an open channel (dashed curve)
corresponding to the ballistic regime.  However, as the trajectories
traverse the geometry, a transition to a super-dispersive case,
especially at low porosities, is evident.  The dashed-dotted line
corresponds has a slope less than 1 indicating the long time behavior of
the trajectories
\begin{align*}
  \sigma_\lambda \sim t^{0.8715}.
\end{align*}

\begin{figure}
\center
\includegraphics*[width =0.55\linewidth]{./figs/100b_second_moment_long_ref}
\caption{\label{fig:Eroding100anomalous} The analysis of anomalous
dispersion in 100 bodies with respect to initial porosity
(as p=50.09\%) and another five porosities during the eroding. The dashed line
correspondes to a porosity of 100\% and the dashed-dotted lines are lines
of best fit with slope 1.1135 (as p=95.12\%), 0.6825 (as p=85.07\%), 
0.7347 (as p=75.14\%), 0.5915 (as p=65.03\%), 
0.6107 (as p=55.02\%), and 0.7 (as p=50.09\%).}
\end{figure}
